### 2015-11-06 CVPR16/Source/experiments2.tex
Fixed the contBBoxModel.tex
Added results from continuous bounding box experiments.

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    initialization                                                                                  & 3.79 & \textbf{0.86} & 1.64 \\
    %$\EnergyLane+\EnergySize+\EnergyBBox+\EnergyDyn                                       $ & 3.83 & 0.90 & \textbf{1.14} \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn                                    $ & 3.83 & 0.90 & 1.14 \\
    %$\EnergyLane+\EnergySize+\EnergyBBoxocc+\EnergyDyn+\EnergyCol                         $ & 3.92 & 0.91 & 1.15 \\
    %$\EnergyLane+\EnergyContpttracks+\EnergySize+\EnergyBBoxocc+\EnergyDyn             $ & 3.81 & 0.92 & 1.59 \\
    % \EnergyBBox+\EnergyDyn+\EnergyCol $
    $\EnergyTrackNoOcc+\EnergyCol + \EnergyLane + \dots$  & 3.80 & 0.91 & 1.58 \\
    $\EnergyTrack+\EnergyCol + \EnergyLane + \dots$ & \textbf{3.78} & 0.91 & 1.58 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
  \label{tab:localizationExperiment}
\end{table}

>>>>

%  seqName   seqNum    Energy_description                                                    windows         t      yaw             dim        
%    City      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  5.811142 0.696358        1.961227        
%    City      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.501543 0.786599        2.375481        
%    City      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  3.932855 0.766397        2.222919        
%    City      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  4.928155 0.806356        2.287911        
% OccCity      1       contPtTracksNoOcc_ctBBoxNoOcc_size_posTmcmc_inference      9/18  3.953464 0.442196        1.720844        
% OccCity      1       contPtTracksNoOcc_contBBoxOcc_size_posTmcmc_inference      8/18  4.815849 0.463034        2.159956        
% OccCity      1       contPtTracks_ctBBoxNoOcc_size_posTmcmc_inference           8/18  4.058560 0.995495        1.593641        
% OccCity      1       contPtTracks_contBBoxOcc_size_posTmcmc_inference           8/18  3.241853 0.631901        2.167446        
% \begin{table}
%   \centering
%   \begin{tabular}{lrrr}
%     \toprule
%     Energy & t & yaw & dim \\
%     \midrule
%     $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$
%     5.81 & 0.69 & 1.96 \\
%     $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$
%     4.50 & 0.78 & 2.37 \\
%     $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$
%     3.93 & 0.76 & 2.22 \\
%     $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$
%     4.92 & 0.80 & 2.28 \\
%     \bottomrule
%   \end{tabular}
%   \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
%   \label{tab:localizationExperimentNoOcc}
% \end{table}
\begin{table}
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    $\EnergyTrackNoOcc + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$ 
    & 3.95 & 0.44  & 1.72\\        
    $\EnergyTrackNoOcc + \EnergyBBox +\EnergySize+\EnergyDyn$        
    & 4.81 & 0.46  & 2.16\\        
    $\EnergyTrack + \EnergyBBoxNoOcc +\EnergySize+\EnergyDyn$      
    & 4.05 & 0.99  & 1.59\\        
    $\EnergyTrack + \EnergyBBox +\EnergySize+\EnergyDyn$             
    & 3.24 & 0.63  & 2.16\\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car. The result provided here are only on occluded tracks}
  \label{tab:localizationExperiment}
\end{table}
